A primer to numerical simulations: The perihelion motion of Mercury

### 2017-12-02 tex/MercuryNumerical.tex
imporved tex infrastructure --- now able to compile without xelatex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt, UK english]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

\usepackage{hyperref}
\usepackage[space=true]{accsupp}
% requires the latest version of package accsupp
\newcommand{\copyablespace}{\BeginAccSupp{method=hex,unicode,ActualText=00A0}\ \EndAccSupp{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Custom
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[T1]{fontenc}           % Embed fonts
\usepackage{textcomp,gensymb}      % \degree

\usepackage{polyglossia}                         % Define languages (Umlaute)
\setdefaultlanguage[variant=american]{english}   % Accent of main language
\setotherlanguage{german}                        % We also have german words
\usepackage[autostyle=true]{csquotes}            % Define quotation style
\MakeOuterQuote{"}                               % Text wrapped in "..." is recognized as a quotation

\usepackage{amssymb}                  % Math stuff
\usepackage{graphicx}                 % Import Pictures + PDFs
\usepackage[svgnames]{xcolor}         % Enabling colors by their 'svgnames'
\usepackage{listings}                 % Code listings  See: https://en.wikibooks.org/wiki/LaTeX/Source_Code_Listings

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt,ngerman,american]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

\usepackage[utf8]{inputenc}         % this is needed for Umlaute
\usepackage[english,ngerman]{babel} % this is needed for Umlaute
\usepackage[T1]{fontenc}            % this is needed for correct output of umlauts in pdf

\usepackage[dvipsnames]{xcolor}         % Enabling colors by their 'svgnames'
\usepackage[%
  unicode=false,%
  pdftitle={A primer to numerical simulations: The perihelion motion of Mercury},%
  pdfauthor={I. Hammer, C. Hanhart, C. Körber and C. Müller},%
  pdfkeywords={Numerical Simulations, Teaching, Perihelion Motion of Mercury, General Relativity},%
  pdfsubject={A primer with the goal to teach general concepts of numerical simulations to high school students.  The specific example is the perihelion motion of mercury due to General Relativity.},   % subject of the document
  colorlinks=true,        % true: colored links
  linkcolor=OliveGreen,          % color of internal links (change box color with linkbordercolor)
  citecolor=magenta,        % color of links to bibliography
  filecolor=YellowGreen,      % color of file links
  urlcolor=blue           % color of external links
]{hyperref}
\usepackage[space=true]{accsupp}
% requires the latest version of package accsupp
\newcommand{\copyablespace}{\BeginAccSupp{method=hex,unicode,ActualText=00A0}\ \EndAccSupp{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Custom
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{textcomp,gensymb}       % \degree

\usepackage[autostyle=true]{csquotes}            % Define quotation style
\MakeOuterQuote{"}                               % Text wrapped in "..." is recognized as a quotation

\usepackage{amssymb}                  % Math stuff
\usepackage{graphicx}                 % Import Pictures + PDFs
\usepackage{listings}                 % Code listings  See: https://en.wikibooks.org/wiki/LaTeX/Source_Code_Listings
